A mechanization of semi-simplicial and semi-cubical sets in the calculus of inductive constructions

### 2022-08-29 paper/paper.tex
paper: wrap Hugo's contrib-para

In the context of typed functional programming, Reynolds'
parametricity~\cite{Reynolds72} interprets types as relations
characterizing the observational equality of programs of this type.
Parametricity can be iterated and it has been noted that iterated
Reynolds' parametricity has a cubical
flavor~\cite{AltenkirchKaposi15,JohannSojakova17,Moulin16,...}. We obtain a
\emph{unary} variant of Reynolds' \emph{binary} parametricity by using
predicates instead of relations, in which case we obtain a form of
(Kreisel) realizability~\cite{Moulin16,BernardyMoulin12}. It has then be
noted that iterated unary parametricity has an augmented simplicial
flavor\footnote{Observation from Hugo Moeneclaey}.

>>>>

In the context of typed functional programming, Reynolds' parametricity~\cite{} interprets types as relations characterizing the observational equality of programs of this type. Parametricity can be iterated and it has been noted that iterated Reynolds' parametricity has a cubical flavor~\cite{}. We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using predicates instead of relations, in which case we obtain a form of (Kreisel) realizability~\cite{}. It has then be noted that iterated unary parametricity has an augmented simplicial flavor\footnote{Observation from Hugo Moeneclaey}.
